Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-05-22 ms.tex
few clarifications of the spec observing log.

We evaluate the stellar parameters by examining the spectra taken with the High Definition Spectrograph (HDS) spectrograph on the Subaru telescope \citep{noguchi2002hds}.
There is one set of data taken on 2013-06-22 (UT) discussed in \citet{kawahara2013starspots}, including 2 exposures each 2700 seconds in duration.
For this 2013 observation, the instrument was configured to use an image slicer unit \#2, which has a resolving power R$\approx$80,000.
Additionally, there are two set of observations from 2015-08-28 (UT) and 2015-08-29 (UT) that were taken to test if the planet could be on a high eccentricity grazing orbit \citep{masuda2018rvKIC1255}, with exposure durations of 2400 seconds each.
The instrument was configured with a 0.3 mm (0.6\arcsec) wide and 30 mm long (60\arcsec) slit, which has a resolving power of R $\approx$60,000.
The second set of observations happened after the reaction wheel failure on 2013-05-11\footnote{\href{https://www.nasa.gov/mission_pages/kepler/news/keplerm-20130521.html}{https://www.nasa.gov/mission\_pages/kepler/news/keplerm-20130521.html}} that ended photometry of the main Kepler field, so no simultaneous Kepler photometry was available with the high dispersion spectroscopy.
The orbital phases during the observations were in the range f
None of the observations was timed during a primary transit (0.0) or secondary eclipse (0.5).

\begin{deluxetable}{cccccccc}
\tablefontsize{\scriptsize}
\tablehead{\colhead{Exposure Number} & \colhead{ExpTime} & \colhead{UT Date} & \colhead{UT Start} & \colhead{Image Slicer} & \colhead{Slit Width} & \colhead{Orbital Phase} & \colhead{Resolving Power}\\
	& (s)	& & & & (mm) & & R}
\startdata
94085 & 2700 &  2013 Jun 22 & 00:32 & 2 & 2.0 & 0.621 & 80,000 \\
94087 & 2700 &  2013 Jun 22 & 00:18 & 2 & 2.0 & 0.670 & 80,000 \\
111345 & 2400 & 2015 Aug 28 & 00:37 & N & 0.3 & 0.667 & 60,000 \\
111349 & 2303 & 2015 Aug 28 & 00:20 & N & 0.3 & 0.712 & 60,000 \\
111355 & 2400 & 2015 Aug 28 & 00:33 & N & 0.3 & 0.790 & 60,000 \\
111359 & 2400 & 2015 Aug 28 & 00:16 & N & 0.3 & 0.835 & 60,000 \\
111373 & 2400 & 2015 Aug 28 & 00:18 & N & 0.3 & 0.901 & 60,000 \\
111525 & 2400 & 2015 Aug 29 & 00:35 & N & 0.3 & 0.194 & 60,000 \\
111529 & 2400 & 2015 Aug 29 & 00:18 & N & 0.3 & 0.240 & 60,000 \\
111533 & 2400 & 2015 Aug 29 & 00:00 & N & 0.3 & 0.285 & 60,000 \\
111549 & 2400 & 2015 Aug 29 & 00:32 & N & 0.3 & 0.382 & 60,000 \\
111553 & 2400 & 2015 Aug 29 & 00:15 & N & 0.3 & 0.428 & 60,000 \\
\enddata
\end{deluxetable}

@@

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/pca_k1255.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/pc1_pc2_acive_quiescent.pdf}
\caption{The principal component eigenvectors scaled by the square root of the eigenvalues (Left), shows that the first component largely describes the extinction while the second and third show the contributions from forward scatterg.
The first two principal components (Right) do not isolate any separate populations of transits.
As expected, the quiescent periods show up as low principal component contributions from both of the two first two eigenvectors (ie. a flatter light curve)}\label{fig:pcaVectorsComp}
\end{centering}
\end{figure*}

>>>>

We evaluate the stellar parameters by examining the spectra taken with the High Definition Spectrograph (HDS) spectrograph on the Subaru telescope \citep{noguchi2002hds}.
There is one set of data taken on 2013-06-22 (UT) discussed in \citet{kawahara2013starspots}, including 2 exposures each 2700 seconds in duration.
For this 2013 observation, the instrument was configured to use an image slicer unit \#2, which has a resolving power R$\approx$80,000.
Additionally, there are two set of observations from 2015-08-28 (UT) and 2015-08-29 (UT) that were taken to test if the planet could be on a high eccentricity grazing orbit \citep{masuda2018rvKIC1255}, with exposure durations of 2400 seconds each.
The instrument was configured with a 0.3 mm (0.6\arcsec) wide and 30 mm long (60\arcsec) slit, which has a resolving power of R $\approx$60,000.
The second set of observations happened after the reaction wheel failure on 2013-05-11\footnote{\href{https://www.nasa.gov/mission_pages/kepler/news/keplerm-20130521.html}{https://www.nasa.gov/mission\_pages/kepler/news/keplerm-20130521.html}} that ended photometry of the main Kepler field, so no simultaneous Kepler photometry was available with the high dispersion spectroscopy.
We list the observing log in Table \ref{}
None of the observations was timed during a primary transit (0.0) or secondary eclipse (0.5).

\begin{deluxetable}{cccccccc}
\tablecaption{List of Spectroscopic Observations}
\tablefontsize{\scriptsize}
\tablehead{\colhead{Exposure Number} & \colhead{ExpTime} & \colhead{UT Date} & \colhead{UT Start} & \colhead{Image Slicer} & \colhead{Slit Width} & \colhead{Orbital Phase} & \colhead{Resolving Power}\\
	& (s)	& & & & (mm) & & R}
\startdata
94085 & 2700 &  2013 Jun 22 & 00:32 & 2 & 2.0 & 0.621 & 80,000 \\
94087 & 2700 &  2013 Jun 22 & 00:18 & 2 & 2.0 & 0.670 & 80,000 \\
111345 & 2400 & 2015 Aug 28 & 00:37 & N & 0.3 & 0.667 & 60,000 \\
111349 & 2303 & 2015 Aug 28 & 00:20 & N & 0.3 & 0.712 & 60,000 \\
111355 & 2400 & 2015 Aug 28 & 00:33 & N & 0.3 & 0.790 & 60,000 \\
111359 & 2400 & 2015 Aug 28 & 00:16 & N & 0.3 & 0.835 & 60,000 \\
111373 & 2400 & 2015 Aug 28 & 00:18 & N & 0.3 & 0.901 & 60,000 \\
111525 & 2400 & 2015 Aug 29 & 00:35 & N & 0.3 & 0.194 & 60,000 \\
111529 & 2400 & 2015 Aug 29 & 00:18 & N & 0.3 & 0.240 & 60,000 \\
111533 & 2400 & 2015 Aug 29 & 00:00 & N & 0.3 & 0.285 & 60,000 \\
111549 & 2400 & 2015 Aug 29 & 00:32 & N & 0.3 & 0.382 & 60,000 \\
111553 & 2400 & 2015 Aug 29 & 00:15 & N & 0.3 & 0.428 & 60,000 \\
\enddata
\tablenotetext{}{Observing log of the Subaru HDS spectroscopic observations.}\label{tab:specObs}
\end{deluxetable}

@@

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/pca_k1255.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/pc1_pc2_acive_quiescent.pdf}
\caption{The principal component eigenvectors scaled by the square root of the eigenvalues (Left), shows that the first component largely describes the extinction while the second and third show the contributions from forward scattering.
The first two principal components (Right) do not isolate any separate populations of transits.
As expected, the quiescent periods show up as low principal component contributions from both of the two first two eigenvectors (ie. a flatter light curve)}\label{fig:pcaVectorsComp}
\end{centering}
\end{figure*}
